%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {GitStart, Remote} % Organization
    {San Francisco, Californie, USA} % Location
    {May 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Opine}
        \item {Vivoo}
        \item {Trophy}
        \item {Cal.com}
        \item {Twenty}
        \item {Directus}
        \item {Spellbound}
        \item {\textbf{Tools}: Javascript - React.js - Vue.js - Next.js - Ruby - Ruby on Rails}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Clora, Remote} % Organization
    {Boston, Massachausetts, USA} % Location
    {March 2022 - January 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed in fixing bugs in Ruby on Rails and React.js}
        \item {Contributed in the re-implementation of the Onboarding process in Ruby on Rails and React.js}
        \item {Implemented some feature interacting with Coresignal API - Sovren (Resume Parsing) in Ruby on Rails}
        \item {Implemented some data science process with Python}
        \item {\textbf{Tools}: Javascript - React.js - Ruby - Ruby on Rails - Python - Scikit Learn}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Skillz, Remote} % Organization
    {San Francisco, Californie, USA} % Location
    {August 2021 - January 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed in the implementation of web features for international project in Ruby on Rails and React.js}
        \item {Involved in the planning of the FastMatch features collaborating with the Product and Engineering teams to understand the overall goals in-
        tended to achieve building the features.}
        \item {Implemented several features in Nx Framework}
        \item {Involved on bug fixing from cloud component detected when implementing some features}
        \item {\textbf{Tools}: Javascript - React.js - Nx - Ruby - Ruby on Rails}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Techinical Support Engineer} % Job title
    {Microverse, Remote} % Organization
    {San Francisco, Californie, USA} % Location
    {March 2019 - November 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reviewing students projects HTML 5/CSS 3, Ruby, Ruby on Rails, Javascript, React.js}
        \item {One to one meeting with students to help them to improve their projects}
        \item {\textbf{Tools}: Javascript - React.js - Node.js - Ruby - Ruby on Rails}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {ITS-NH} % Organization
    {Yaounde, Centre, Cameroon} % Location
    {June 2019 - January 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a hybrid mobile application using Flutter.}
        \item {Built a API layer of a web application using Django.}
        \item {Design of the BI architecture for the Financial App Department.}
        \item {\textbf{Tools}: Dart - Flutter - Python - Django - Pentaho}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst} % Job title
    {EGPAF Cameroon} % Organization
    {Yaounde, Centre, Cameroon} % Location
    {August 2018 - December 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed in data verification and validation and implemented the corresponding SOP.}
        \item {Collected and transferred data periodically after cleaning and transforming them.}
        \item {Analyzing data for the manager to ease their presentation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-founder, Lead Software Engineer} % Job title
    {N'KAP SI SARL} % Organization
    {Yaounde, Centre, Cameroon} % Location
    {August 2017 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Setting up of automatic data collection concerning the needs of users mentioned on social networks.}
        \item {Building a machine learning model for taxi price prediction - Integration on the N'kap Si platform.}
        \item {Building of the N'Kap Si platform.}
        \item {N'kap Si Android application (play.google.com/store/apps/details?id=com.nkapsi) already available on Play Store.}
        \item {\textbf{Tools}: Docker - Android - Angular - Node.js - MongoDB - RabbitMQ - Python - Tensorflow}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst, Software Engineer} % Job title
    {Centre Pasteur du Cameroun} % Organization
    {Yaounde, Centre, Cameroon} % Location
    {August 2015 - March 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementation and Management of a data collection system based on smartphones.}
        \item {Built platform for surveillance epidemiological using on R, R-Shiny, Java for backend, MongoDB.}
        \item {Monitored and managed of data collected via smartphones.}
        \item {Data Quality Assurance and Periodic Activity Report.}
        \item {Development of data analysis scripts on R.}
        \item {Participation in the development of an automatically updated dashboard and offering pre-defined analyzes.}
        \item {Built ETL with Pentaho for integrating several databases into one and running at regular time intervals.}
        \item {\textbf{Tools}: Angular - Node.js - MongoDB - Java - R - R Shiny - Python - Apache Spark - D3.js - Pentaho}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Consultant} % Job title
    {Express Exchange S.A.} % Organization
    {Douala, Littoral, Cameroon} % Location
    {September 2014 - August 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimisation of the BI platform previously built}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Developer} % Job title
    {Orange Cameroon S.A.} % Organization
    {Douala, Littoral, Cameroon} % Location
    {September 2014 - August 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and provisioned of dashboards for the customers departements.}
        \item {Optimized of existing dashboards using QlikView.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Intelligence Consultant} % Job title
    {Express Exchange S.A.} % Organization
    {Douala, Littoral, Cameroon} % Location
    {September 2014 - August 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Proposed a BI platform to the company.}
        \item {Gathered the business need for a BI system.}
        \item {Built a data warehouse and a Business Intelligence system.}
        \item {\textbf{Tools}: Microsoft BI Stack - Python - Apache Spark - D3.js}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Entry} % Job title
    {Programme National de Lutte contre la Tuberculose (PNLT)} % Organization
    {Yaounde, Centre, Cameroon} % Location
    {June 2013 - July 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Entered data collected thought CSPro application.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
